% Project proposal report
% 
% Authors: Michael Galliers and James Miller
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}


% Document configuration

% Section numbering
\renewcommand \thesection{\Roman{section}}
\renewcommand \thesubsection{\arabic{section}.\arabic{subsection}}
% Do paragraph indenting after section tags
\usepackage{indentfirst}


\usepackage[usenames, dvipsnames]{color}
\author{Michael Galliers and James Miller}
\title{CSC 440 - Project Proposal}
\date{August 20, 2019}


\begin{document}

\begin{titlepage}
\maketitle
\end{titlepage}

\tableofcontents

% \section{Introduction}

\section{Project Overview}
For our team and individual projects in CSC 440 this Fall semester, we have decided to make a grade
tracking web application. Our proposed name for the project is \textbf{\{Insert Awesome Name\}}.

\subsection{Problems and Needs}
This idea arose from personal experience, not being able to effectively manage grades from various
courses on BlackBoard. This can be due to professors not using BlackBoard to manage grades or the
inability of BlackBoard to correctly aggregate students grades because of an odd grading policy.
This makes it difficult for students to track how well they are doing in a course overall. As a
result, students can be more or less likely to study hard for assignments, since they believe they
are doing worse or better in the course than they actually are.

For those who decide to manage their grades themselves with pen and paper, they are able to gain
further insight into their performance in courses, but are limited by the amount of time it takes to
manage and compute statistics about their grades. As a student, there should be a simple way to
manage and visualize grades, without the need to do calculations by hand.

\subsection{System Requirements}
As a solution to these problems, we propose a web based software application. This application shall
include, but not be limited to, the following requirements:
% We propose a software solution to these
% As a solution to this problem we propose building a grade tracking web application including, but
% not limited to, the following features:

\begin{itemize}
    \item Allow a student to create, retrieve, update and delete semesters.
    \item Allow a student to create, retrieve, update and delete courses in each semester.
    \item Allow a student to create, retrieve, update and delete grading categories in each course.
    (e.g. homework, tests, etc.).
    \item Allow a student to create, retrieve, update and delete grade entries in each category.
    \item Allow different grading strategies to be used for each course, i.e. total point based vs.
    weight based.
    \item Account for additional grading requirements (e.g. to get an 'A' you need at least a 90\%
    overall and at least 80\% in each category).
    \item Include visualizations/summaries for how well a student is doing in a course, category or
    the semester overall.
    \item Include a "What If" feature, allowing a student to see how a score on a particular
    assignment would effect his/her overall grade.
\end{itemize}

\section{Goals}
\subsection{Project}
In building this project, we intend to use a modern software development stack. As a result, our
team will strive to gain knowledge in the following technologies/principals:

% In working on this project, we intend to use modern/relevant open source software
% languages/frameworks, management techniques and dev-ops principals. These include:

\begin{itemize}
    \item React.js and Javascript for the frontend
    \item Python for the backend
    \item JetBrains development IDEs
    \item Continuous Integration and Continuous Development (CI/CD)
    \item Container-based application deployment
\end{itemize}

\subsection{Product}

\section{System Workflow}

\section{Required Resources}
\subsection{Hardware}
For deployment of our application, we are planning on utilizing cloud based computing hardware for
running the application backend, serving the frontend, and managing the database. Our final decision
on a specific cloud provider is subject to change, but the online service \textit{Digital Ocean} is
a possibility. It offers reasonable pricing and should allow us to run the application for a minimal
amount of cost.

\subsection{Software}
To build the we plan on using a modern software development stack. This includes the following
software/technologies:

\begin{itemize}
    \item React.js and Javascript for the frontend
    \item Python for the backend
    \item JetBrains development IDEs
    \item Git with GitHub for source control
    \item GitHub-integrated CI service for automatic building and deploying
    \item Docker/Kubernetes for scalable containerized deployments
    \item PostgreSQL relational database for storing data
\end{itemize}

\section{Dictionary}
\begin{itemize}
    \item \textbf{Semester}: A single semester of education consisting of courses. Each semester can
    be associated with a different educational institution; consistency is not required.
    \item \textbf{Course}: Any educational course/class occurring within a particular semester.
    \item \textbf{Section}: An equally weighted or logically grouped collection of material within a
    particular course (e.g. Homework, Tests, etc.).
    \item \textbf{Grade Entry}: A graded item for a particular section (e.g. Homework 2, Exam 1,
    etc.).
\end{itemize}


% \section{Problem and Needs}

% \section{Solution}


\end{document}
